---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# batchr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.com/poissonconsulting/batchr.svg?branch=master)](https://travis-ci.com/poissonconsulting/batchr)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/batchr?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/batchr)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/batchr/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/batchr?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

`batchr` is an R package to batch process files using an R function.

The key design principle is that only files which were last modified *before*
the directory was 'configured' are considered for processing.
To implement this principle, configuration creates a hidden file and 
existing successfully processed files are automatically 'touched' to update 
their modification date.

This design means that:

- Batch processing can be stopped and restarted.
- Any files created during processing are ignored.

To allow the user control over the reprocessing of problematic files 
all processing attempts (SUCCESS or FAILURE) are recorded in a hidden log file.

## Installation

You can install the latest development version of batchr from [GitHub](https://github.com/poissonconsulting/batchr) with:

``` r
# install.packages("remotes")
remotes::install_github("poissonconsulting/batchr")
```

## Demonstration

Consider a directory with two .csv files

```{r}
path <- file.path(tempdir(), "example")
unlink(path, force = TRUE)
dir.create(path)

write.csv(data.frame(x = 1), file.path(path, "file1.csv"), row.names = FALSE)
write.csv(data.frame(x = 3), file.path(path, "file2.csv"), row.names = FALSE)
```

First define the function to process them.

```{r}
fun <- function(file) {
  data <- read.csv(file)
  data$x <- data$x * 2
  write.csv(data, file, row.names = FALSE)
  TRUE
}
```

Then simply call `batch_process()` to apply the function to all the files.

```{r}
library(batchr)
batch_process(fun, path, ask = FALSE)
```

The files have been updated as follows.

```{r}
read.csv(file.path(path, "file1.csv"))
read.csv(file.path(path, "file2.csv"))
```

For a more realistic demonstration with finer control over the batch processing see the [Batchr Demonstration](https://poissonconsulting.github.io/batchr/articles/batchr-demo.html) vignette.

### Parallel Chains

To process the files in parallel:

1) Ensure plyr and doParallel are installed using `install.packages(c("plyr", "doParallel"))`.
2) Register a parallel backend using `doParallel::registerDoParallel(4)`.
3) Set `parallel = TRUE` in the call to `batch_process()` or `batch_run()`.

### `batch_gsub()`

The `batchr` package also provides `batch_gsub()` to perform text replacement on multiple files.

## Contribution

Please report any [issues](https://github.com/poissonconsulting/batchr/issues).

[Pull requests](https://github.com/poissonconsulting/batchr/pulls) are always welcome.

Please note that the 'batchr' project is released with a [Contributor Code of Conduct](https://poissonconsulting.github.io/batchr/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.
