---
title: "Get Started with batchr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started with batchr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Consider a temporary directory with four txt files

```{r}
path <- file.path(tempdir(), "demo")
unlink(path)
dir.create(path)

writeLines("the contents of file.txt", file.path(path, "file.txt"))
writeLines("the contents of file2.txt", file.path(path, "file2.txt"))
writeLines("the contents of file3.txt", file.path(path, "file3.txt"))
writeLines("the contents of file4.txt", file.path(path, "file4.txt"))
```

and a function that will successfully process the first two files 
(in this case rewriting their contents)
but fail for the last two by returning FALSE and throwing an error, respectively.

```{r}
fun <- function(file) {
  if(grepl("file3[.]txt$", file)) return(FALSE)
  if(grepl("file4[.]txt$", file)) stop("Uh, Houston, we've had a problem.", call. = FALSE)
  txt <- readLines(file)
  txt <- gsub("contents", "modified contents", txt)
  writeLines(txt, file)
}
```

## Configure

Now let the user configure the directory to only process files names that include
a digit before the file extension.
```{r}
library(batchr)
print(batch_config(fun, path = path, regexp = "file\\d[.]txt$"))
```

The contents of the hidden figuration file are as follows
```{r}
batch_config_read(path)
```
The `time` value specifies the system time (in UTC) that the project was configured.
It is very important because only files that were last modified *before* the configuration time are considered to be unprocessed (when a file is successfully processed its modification time is automatically set to the current system time).

## Run

With the directory configured the next task is to start processing the files
```{r}
print(batch_run(path, ask = FALSE))
```

From the output we can see that 'file2.csv' was processed successfully but
processing of the other two files that matched regexp failed.
The output is also recorded in a hidden log file that can be read using `batch_log_read()`.
```{r}
batch_log_read(path)
```

or summarised using
```{r}
batch_report(path)
```

The contents of 'file2.csv' are now as follows
```{r}
readLines(file.path(path, "file2.txt"))
```

## Reconfigure

At this point let us update the function and regular expression so that 
all files are included and successfully processed.
```{r}
batch_reconfig_fileset(path, regexp = "[.]txt$")

fun <- function(file) {
  txt <- readLines(file)
  txt <- gsub("contents", "modified contents", txt)
  writeLines(txt, file)
}

batch_reconfig_fun(path, fun)
```

## Rerun

Now when we call `batch_run()` the newly included 'file.txt' is successfully processed.
```{r}
batch_run(path, ask = FALSE)
```

```{r}
batch_report(path)
```

In order to reattempt processing of the 'file3.txt' and 'file4.txt' we need
to set `failed = TRUE`.

```{r}
batch_run(path, failed = TRUE, ask = FALSE)
```

```{r}
batch_report(path)
```

## Clean Up

With all the files successfully processed the only remaining task is to 
delete the hidden configuration and log files.

```{r}
list.files(path, all.files = TRUE)
print(batch_cleanup(path))
list.files(path, all.files = TRUE)
```
